---
author: "Michael Karp"
title: "Quiz 3 - Getting and Cleaning Data - Data Science Specialization"
date: 1/18/2014
output: 
html_document:
keep_md: true
---

## Loading and preprocessing the data
```{r, echo = TRUE, results='asis'}
if(!file.exists("./data")){dir.create("./data")}
fileUrl1 = "https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Fss06hid.csv"
download.file(fileUrl1,destfile="./data/housing.csv",method="curl")
housing = read.csv("./data/housing.csv")
# Inspect Data
str(housing)
summary(housing)
```

# q1 - Identify first 3 rows of where 10+ acres were sold and 10K+ worth of product were sold
```{r, echo = TRUE, results='asis'}
tenplusacres_tenplusproducts <- which(housing$ACR == 3 & housing$AGS == 6)
tenplusacres_tenplusproducts[1:3]
```
# q2 - Use the parameter native=TRUE. What are the 30th and 80th quantiles of the resulting data? (some Linux systems may produce an answer 638 different for the 30th quantile)
```{r, echo = TRUE, results='asis'}
library(jpeg)
img_name <- "/Users/MKarp/datasciencecoursera/Getting and Cleaning Data/data/getdata-jeff.jpg"
img <- readJPEG(img_name, native = TRUE)
# 30th and 80th quantiles
quantile(img,probs=c(0.3,0.8))
```

# q3 - Match the data based on the country shortcode. How many of the IDs match? Sort the data frame in descending order by GDP rank (so United States is last). What is the 13th country in the resulting data frame? 
```{r, echo = TRUE, results='asis'}
if(!file.exists("./data")){dir.create("./data")}
fileUrl2 = "https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FGDP.csv"
fileUrl3 = "https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FEDSTATS_Country.csv" 
download.file(fileUrl2,destfile="./data/gdp190.csv",method="curl")
download.file(fileUrl3,destfile="./data/education190.csv",method="curl")
gdp190 = read.csv("./data/gdp190.csv")
education190 = read.csv("./data/education190.csv")
str(gdp190)
str(education190)
names(gdp190)[1:5] <- c("CountryCode","Gross.domestic.product.2012","GDP.Rank", "Long.Name", "gdp")
mergedData = merge(gdp190,education190, by = "CountryCode")
str(mergedData)
head(mergedData)
# change the GDP values to numeric
mergedData$Gross.domestic.product.2012 <- as.numeric(mergedData$Gross.domestic.product.2012)
# how many were matched
matched <- sum(!is.na(unique(mergedData$GDP.Rank)))
head(mergedData[order(GDP.Rank, decreasing = TRUE),13) 
head(mergedData, 13)

```

mergedData[, mean(rankingGDP, na.rm = TRUE), by = Income.Group]




